\documentclass{swfcthesis}
\usepackage{multicol}
\begin{document}

\Title{网络用户管理模块的设计与集成}	% 论文标题
\Author{温俊瑞} 	% 作者姓名 
\Advisor{孙永科}      %指导教师姓名
\AdvisorTitle{讲师} %指导教师职称
\AdvisorInfo{孙永科，男，1980年出生，硕士，讲师，计算机科学与
术专业。主要从事软件开发和计算机网络的教学工作，
主讲课程为《计算机网络》，《网络程序设计与开发》
。参加科技部重大科技工程“西南野生生物物种质资源库
”子课题“西南野生生物种质资源库信息系统”的开发
工作；参加科研项目《运用现代教育技术的实践与成果
》获云南省二等奖；参加科研项目《树木学教育教学建设与研究》获云南省二等奖。}	%指导教师简介（约百余字）
\Month{五}		    %月份（比如 六）
\Year{二〇一四} 	    %年份（比如 二〇一二）
\Univ{西南林业大学}    		%校名
\School{计算机与信息学院}		%院系名称
\Subject{计算机科学与技术专业}	%专业名称（比如 电子信息工程专业）
\Docname{本科毕业（设计）论文}	%本科？研究生？
\Abstract{
  如今，一走进咖啡厅、休闲娱乐场所、银行展会、美容购物等地方或者入住酒店时，几乎每个人都会先问一句：有
  没有免费的WiFi啊？WiFi普及的速度着实令人惊叹，已经成为不少人主要的移动上网方式。国外咖啡厅，
  购物商场，酒店等基本都覆盖了wifi热点，顾客利用闲暇时间可以免费上网，同时商家又可以借助弹出的认证
  界面投送广告，带来商业利益。wifi热点认证收到国外很多商家的青睐。就连不少航空公司的航班上
  都开始提供起WiFi服务，让乘客可以利用自带的电脑等电子产品联网，在空中享受发邮件、传递数据
  等。
  
  目前国内WIFI热点认证方案主要还是通过手机短信认证、人工操作认证、采用固定密码或者直接不认
  证。
  
  手机短信认证方式是这样的，用户接入WIFI热点后手机会弹出认证界面，输入手机号码后点击
  获取密码，输入短信中显示的密码即可上网。这样的认证方式存在一些不足，比如用户自带电脑不用手
  机获取密码就无法上网，而且不能有效的防止蹭网现象的发生，如果用一些软件批量获取密码上
  网的话路由器将会不堪重负。
  人工操作可以防止软件恶意批量新建帐号，但是操作起来耗费人力物力，操作人员也可能因为误操作
  导致网络出问题。
  采用固定密码或者直接不认证的方式就相当于完全公开网络，同样不能防止蹭网。
  
  经过市场调查分析，国内WIFI热点认证方案或配置麻烦或不够安全稳定，基本都是基于windows操作
  系统下来进行控制，人工操作环节比较多从而导致费时费力。本文介绍了一套基于Raspberry Pi\cite{pie}的
  WIFI热点认证方案，通过集成于Raspberry Pi实现刷卡打印的功能，为人们在商业场所、酒店、机场
  等热点认证提供便利。通过PYTHON程序在后台来控制Router OS\cite{routeros-book}上的用户自动化认证，无需人工操作，
  用户只需要通过刷卡然后打印机自动打印上网用户名和密码，用户使用该密码便可以上网。认证弹出的界面可以投放广告，
  为商家带来利益。另外安装配置方便，配置完成后安全稳定，减少了工作人员的工作力度。
}	%论文摘要（约两百字）
\Keywords{Raspberry Pi，刷卡，打印，Router OS，WIFI，热点认证}	%关键字（比如 电阻, 电容, 电感, 电灯泡）
\Acknowledgments{非常感谢在大学期间的各位老师教授了我很多东西，并且在学习和生活中给予了我
  很大帮助，在这四年期间，我学到了很多在学校外面学不到的东西，在何鑫老师和和辛宏老师的启蒙
  下我开始喜欢上编程，接触到了面向对象、MVC的思想，打好了编程的基础，非常感谢他们。还要感谢王晓林老师让我很幸运地接
  触到了世界上最好玩的系统和编辑器。还要感谢孙永科老师，在您的带领下我试着自己
  尝试创造很多有趣的东西，通过动手实践我学会了很多网络知识，喜欢上了PYTHON
  ，学会了把书本知识应用到每一个有趣的项目里，从研发产品，再到售前售后懂得了如何制定研发计
  划，和客户沟通改善用户体验，非常感谢您。另外还有很多我们学院的优秀老师给予了我很大的帮助，谢谢你们。}		%鸣谢 （感谢人民感谢党，约百字）
\enTitle{Design and Integration of Network User Management Module}			%英文标题
\enAuthor{rory}			%作者英文姓名
\enUniv{Southwest Forestry University}	%英文校名
\enSchool{School of Computer and Information Science}	%英文院系名称
\enAbstract{Nowadays, when people go to Café, Entertainment, Bank Show, Beauty Shopping, hotel
  and other Entertainment places, almost everybody will ask if there is free WIFI? Universal
  speed of the WIFI is indeed amazing, and has become a major way of mobile
  Internet. Foreign cafes, shopping malls, hotels and other entertainment venues are
  basically covered with WIFI hotspots, customers can access free in their spare time, 
  while businesses can make use of pop-up and delivery of advertising authentication
  interface to get commericial interests. WIFI hotspot authentication is very popular
  between businesses in foreign countries. Even on many airlines have begun to offer
  services of WIFI hotspot, so that passengers can surf the internet with their computers
  or other electronic products, enjoy e-mail in the air, passing data and so on.

  Currently WIFI hotspot authentication scheme mainly via SMS certification, certification
  with manual operation, using a fixed password or no certification. SMS authentication
  method is that after the user accessed WIFI, hotspot authentication interface will pop
  up the phone, enter the phone number after clicking Obtain the password, enter the
  password to access Internet. There are some deficiencies of this king of authentication,
  such as a user can not access Internet without a Phone, and can not effectively prevent
  the occurrence of rubing network, if some malware bulk access to the Internet, then the
  router will be overwhelmed. Manual operation can prevent malicious software, but the
  operation cost of manpower and resources, the operator may cause network problems
  because of misuse. Fixed password or no authentication provides an easy way for everyone to rub
  network.

  After market research analysis, domestic WIFI hotspot authentication sch-emes either
  complicated in configuration or insufficient in security and stability, which are mostly
  based on windows operating System, manual operation links leading to more
  time-consuming. This paper introduces a set based On Raspberry Pi \cite{pie} of WIFI
  hotspot authentication scheme, Raspberry Pi are integrated with brushing-card printing
  function, providing people with convenient hotspot certification in commercial
  establishments, hotels and airports. Router OS\cite{routeros-book} is controlled by
  PYTHON program for the automate user authentication in the background. Without manual
  operation, Users only need to Brush card and then the printer automatically prints the
  username and password, the user will be able to access by this username and
  password. Authentication pop-up interface can advertise, which Benefits businesses. It
  is easy to install and configure, the system is highly security and stability, reducing
  the efforts of the staff.  }  %论文英文摘要
\enKeywords{Raspberry Pi, Brush cards, Router OS, WIFI, hotspot} %英文关键字

%%% 下面六行不要动！
\makepreliminarypages
\frontmatter
\tableofcontents
\listoffigures
\listoftables
\mainmatter
%%% 上面六行不要动！

%%% 正文开始

\include{chapters/Introduction} %%前言
%\include{chapters/Chapter2}  %%设计背景和意义（不要了）
%\include{chapters/Chapter3}  %%目标问题 （不要了）
\include{chapters/Chapter4}  %%研究方案
\include{chapters/Chapter5}  %%方案实施
\include{chapters/Chapter7}  %%配置ROS路由器(调整了一下位置，更合理)
\include{chapters/Chapter6}  %%网络拓扑设计
\include{chapters/Chapter8}  %%软件方案设计
\include{chapters/shigongtu} %%施工图

%%% 正文部分到此结束。下面是『参考文献』、『指导教师简介』、『鸣谢』、『附录』
\Appendix{} % 不要动这一行！
% 下面是参考文献部分
\begin{thebibliography}{99}
\bibitem{wifi-hotspot} Geier, Eric. Wi-Fi Hotspots. Cisco Press, 2006.
\bibitem{pi-start} Richardson, Matt, and Shawn Wallace. Getting Started with Raspberry
  Pi. O'Reilly Media, Inc., 2012.
\bibitem{pi-guide} Halfacree, Gareth, and Eben Upton. Raspberry Pi User Guide. John Wiley
  \& Sons, 2012.
\bibitem{pi-python} Monk, Simon. Programming the Raspberry Pi: Getting Started with
  Python. McGraw-Hill, 2013.
\bibitem{routeros-book} 崔北亮.《Router OS 全攻略》，电子工业出版社. 2010.
\bibitem{py-ref} Beazley, David M. Python essential reference. Addison-Wesley
  Professional, 2009.
\bibitem{wxpy-act} Rappin, Noel, and Robin Dunn. wxPython in Action. Manning, 2006.
\bibitem{pie} Raspberry Pi Quick Start Guide,
  \url{http://www.raspberrypi.org/help/quick-start-guide/}
\bibitem{wikipedia-pie}Wikipedia: Raspberry Pi,
  \url{http://en.wikipedia.org/wiki/Raspberry_Pi}
\bibitem{ros} Wikipedia: MikroTik, \url{http://en.wikipedia.org/wiki/MikroTik}
\bibitem{wxpython} Wikipedia: WxPython, \url{http://en.wikipedia.org/wiki/WxPython}
\bibitem{termio} Termio Manual, \url{http://man7.org/linux/man-pages/man7/termio.7.html}
\end{thebibliography}

\advisorinfopage{} % 不要动这一行！
\acknowledgmentspage{} % 不要动这一行！

%%% 下面是附录部分。

\include{chapters/appendix}   % 附录

\end{document} % 此行后面不要有任何文字。

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
